---
title: "Docker Deployment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Docker Deployment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

ReviewR is designed to support multiple concurrent users when deployed using Shiny Server. In server deployments, users will access ReviewR directly through a web browser without requiring a local R installation. When deployed on a centralized server an instance of ReviewR will be served to each connecting user in distinct R sessions allowing multiple participants to simultaneously connect to patient data and submit chart abstraction information. 

### Docker

ReviewR also ships with a Dockerfile, simplifying the deployment process. The Dockerfile will install R, Shiny, and all the necessary dependencies needed to run ReviewR. To start:

1. Fork the ReviewR repository to the home directory of your server. This can be done from the **R console** with the `usethis` package: 
    ```{r eval=FALSE}
    # install.packages('usethis')
    usethis::create_from_github(repo_spec = 'thewileylab/ReviewR', destdir = '~/')
    ``` 
2. Using the **bash terminal**, run:
    ```{bash eval=FALSE}
    cd ~/ReviewR
    docker build --tag reviewr:latest .
    docker run --publish 1410:1410 --detach --name ReviewR reviewr:latest
    ```

That's it! ReviewR can now be accessed from your browser at http://your.shinyserver.ipaddress:1410 . In order to encrypt this connection, be sure to reverse proxy port 1410 to your server's URL.