---
title: "Server Deployment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Server Deployment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Shiny Server OSE
ReviewR is designed to support multiple users through the use of Shiny Server. When deployed, Shiny Server will serve an instance of ReviewR to each user in their own separate R session.

1. Follow the [Shiny Server Quick Start Guide](https://support.rstudio.com/hc/en-us/articles/360011458854-Shiny-Server-Quick-Start-Installation-and-Configuration) to get Shiny Server up and running. 
2. Next, clone the ReviewR repository to the home directory of your server. This can be done from the R console with the `usethis` package: 
```{r eval=FALSE}
# install.packages('usethis')
usethis::create_from_github(repo_spec = 'thewileylab/ReviewR', destdir = '~/')
```
3. Finally, using the terminal, create a  symlink from the cloned repository to the `/srv/shiny-server/` directory on your server.
```{bash eval=FALSE}
ln -s ~/ReviewR /srv/shiny-server/ReviewR
```

That's it! ReviewR can now be accessed from your browser at http://your.shiny.server.ip:3838/ReviewR

## Docker
ReviewR also ships with a Dockerfile, simplifying the deployment process. The Dockerfile will install R, Shiny, and all the necessary dependencies needed to run ReviewR. To start:

1. Clone the ReviewR repository to the home directory of your server. This can be done from the R console with the `usethis` package: 
```{r eval=FALSE}
# install.packages('usethis')
usethis::create_from_github(repo_spec = 'thewileylab/ReviewR', destdir = '~/')
``` 
2. Using the terminal, run:
```{bash eval=FALSE}
cd ~/ReviewR
docker build --tag reviewr:latest .
docker run --publish 8100:8100 --detach --name ReviewR reviewr:latest
```

That's it! ReviewR can now be accessed from your browser at http://your.shiny.server.ip:8100

***

*Note, if using the BigQuery module to connect to a Google BigQuery database with a server deployment, additional configuration is required. Please ensure that you meet the following minimum requirements:*

* *Server hosting ReviewR has a configured fully qualified domain name*
* *A Google Project with a configured [Auth 2.0 Client ID for a Web Application](https://developers.google.com/identity/protocols/oauth2/web-server)*
* *Updated ReviewR/R/mod_database_bigquery.R with your OAuth Client ID and Secret*
