---
title: "Local Deployment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Local Deployment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

If you would like to perform a chart review from your local machine, or just simply want to see what ReviewR is all about then a "Single User Deployment" is a good option to start with. ReviewR is an R Shiny application that has adopted the R package framework, thanks to the excellent [golem package](https://thinkr-open.github.io/golem/) developed by [ThinkR](https://github.com/ThinkR-open). As such, installing and running ReviewR should be a breeze! 

## Installation

To install the latest development release:
```{r eval=FALSE}
# install.packages('devtools')
devtools::install_github('thewileylab/ReviewR')
```


## Usage

Now that ReviewR is installed the application can be launched by running:

```{r eval=FALSE}
ReviewR::run_app()
```

