---
title: "REDCap API Exploration - Data Insertion"
author: "David Mayer"
date: "2/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(redcapAPI)
library(tidyverse)
library(magrittr)
```

## Create a REDCap connection
```{r}
api_url <- 'https://redcap.ucdenver.edu/api/'
api_token <- readline("Enter REDCap Project API Token:")
rcon <- redcapConnection(url = api_url, token = api_token)
```


## Can we add additional records?!
Here, we load a CSV file with all of the required fields, but with some weridness added
```{r eval=FALSE, include=FALSE}
push_to_REDcap <- read_csv(file = 'push_to_REDcap_4.csv')
importRecords(rcon = rcon, data = push_to_REDcap,)
```

## Note on Sliders
Values cannot be exported when entered using the REDcap instrument. Oddly, you can store information in the slider field when importing records from a data.frame, and they will then be returned from the `exportRecords` command.

## Note on Comment fields
You can break this API call if there are invalid (unexpected?) characters in the`ice_cream_comments` field. See push_to_REDcap_3.csv, participant 6. Entries show up on the web, minus the invalid characters but can no entries can be recieved from the API call. 

## Overwrite Behavior
When supplying a dataframe to the 'importRecords()' function you can define 2 different overwrite behaviors. 
* overwriteBehavior='normal'
** Blank information in supplied dataframe will not overwrite information that has already been pushed to REDcap
* overwriteBehavior='overwrite'
** Blank information in supplied dataframe will overwrite information that has been already pushed to REDcap (blanks it)
* In all cases, new information supplied to REDcap (not NA) will overwrite information that has already been pushed to REDcap.

## What if columns are missing?
```{r}
push_to_REDcap <- read_csv(file = 'push_to_REDcap_5.csv')
importRecords(rcon = rcon, data = push_to_REDcap)
```

Information is uploaded where available. Required fields are not "required" when uploading data through the API

## Input Validation
in a multiple choice scenario, if an invalid choice is selected, nothing will get pushed to REDCap.

```{r}
push_to_REDcap <- read_csv(file = 'push_to_REDcap_4.csv')
importRecords(rcon = rcon, data = push_to_REDcap)
```

## SQL Injection?
