---
title: "REDCap API Exploration - Data Extraction"
author: "David Mayer"
date: "2/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(redcapAPI)
library(tidyverse)
library(magrittr)
```

## Create a REDCap connection
REDCap Connections take two arguments, your institution' redcap API access url and an API token, which is generated per project.
```{r}
api_url <- 'https://redcap.ucdenver.edu/api/'
api_token <- readline("Enter REDCap Project API Token:")
rcon <- redcapConnection(url = api_url, token = api_token)
```

## Did the Connection work?
```{r}
exportUsers(rcon)
```
Indeed it did.

## What other information can we get from the API?
```{r}
exportProjectInformation(rcon)

```

## REDcap Verison?
```{r}
exportVersion(rcon)
```
This ends up being important. Exporting values from REDcap sliders is not supported in versions 6.5.0+

## Dictionary Info? Question Types for the project?
Yes, project meta data can be exported. If more than one instrument is defined, supply the `form=` option to only export the information that is relevant to the instrument you are working with.
```{r}
meta <- exportMetaData(rcon)
meta
```

```{r}
unique(meta$field_type)
```

## Are there any records present?

Note: You can break this API call if there are invalid (unexpected?) characters in the`ice_cream_comments` field. See push_to_REDcap_3.csv, participant 6. Entries show up on the web, minus the invalid characters but can no entries can be recieved from the API call. 
```{r}
records <-exportRecords(rcon)
records
```

### Note on Sliders
Values cannot be exported when entered using the REDcap instrument. Oddly, you can store information in the slider field when importing records from a data.frame, and they will then be returned from the `exportRecords` command.

## Bundle
```{r, include=F}
bundle <- exportBundle(rcon, date = TRUE, label = TRUE, meta_data = TRUE, users = TRUE, instruments = TRUE, events = TRUE, arms = TRUE, mappings = TRUE, version = TRUE)
```
If you want to know a lot of things ad don't have a lot of time. This will store most of the project metadata as a list object.

