---
title: "Table Map Function Exploration"
author: "David Mayer"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(RPostgres)
library(bigrquery)

# For Testing... would be pulled from elsewhere in the Shiny App
  wd <- '/Users/MayerDav/R_Projects/ReviewR_Internal'
  project_id <- "class-coursera-dev"
  con <- DBI::dbConnect(drv = bigquery(),
                        project = project_id,
                        dataset = "synpuf1k_omop_cdm")
  
  db_type = "BigQuery"
  user_data_model = "omop"
  user_model_version = "v6_0"
```

## Detect and load supported models
Poll a directory containing OMOP and MIMIC table mappings either downloaded or developed from their respective GitHub pages. Do some light processing on the file names and directory structure to extract important information:
* Model Type
* Model Version
* Read supported data model
```{r prep}
# Load all the models we support. Process the file path and file name to determine model type and version (hopefully) 
  models <- list.files(path = file.path(wd,"models"),full.names = T,recursive = T) %>% 
    tibble(file_path = .) %>% 
    mutate(data_model = str_extract(string = file_path, pattern = regex('(mimic3)|(omop)',ignore_case = T)),
           data_model = tolower(data_model),
           model_version = basename(file_path),
           model_version = str_replace(string = model_version, pattern = regex(pattern = '(mimic3)(_)?|(omop_cdm_)',ignore_case = T),replacement = ''),
           model_version = str_replace(string = model_version, pattern = regex(pattern = '.csv',ignore_case = T),replacement = ''),
           model_version = tolower(x = model_version),
           cdm = map(.x = file_path,.f = read_csv, col_types = cols()),
           cdm = map(.x = cdm,.f = select, c("table","field"))
          )
  models #Preview
```

## Filter based on user input
```{r}
  ## Filter either OMOP or MIMIC
  potential_models <- models %>%
    filter(data_model == user_data_model)
  potential_models
```

## Can we detect the data model verion of the user's data?
```{r}
  ## Load user tables and nest fields
  user_tables <- dbListTables(con) %>% 
    tibble(user_database_table = .) %>% 
    mutate(user_fields_long = map(.x = user_database_table,.f = dbListFields,conn=con),
           user_fields_long = map(.x = user_fields_long,.f = as.tibble)
    )
  ## Unnest and coerce to match cdm standards
  user_tables %<>% 
    unnest() %>% 
    rename(user_fields = value) %>% 
    mutate(clean_user_fields = tolower(user_fields),
           clean_user_fields = str_replace(string = clean_user_fields, pattern = regex(pattern = '[.!?\\-]'),replacement = '_'),
           clean_table = tolower(user_database_table),
           clean_table = str_replace(string = clean_table, pattern = regex(pattern = '[.!?\\-]'),replacement = '_')) %>% 
    select(user_database_table, clean_table, user_fields, clean_user_fields)
  user_tables
```
## Match the user data with all of the suported CDM's
```{r}
  ##join-tastic
  potential_models %<>%
    mutate(join = map(.x = cdm,.f = left_join, user_tables, by = c("table"= "clean_table","field"="clean_user_fields")))
  potential_models
```

## Count the number of table/field pairs from CDM vs User data
```{r}
   #purr
  check_it <- potential_models %>% 
    mutate(filtered = map(.x = join,.f = filter, is.na(user_fields)!=T),
          count_filtered = map(.x = filtered,.f = nrow), 
          count_filtered = unlist(count_filtered)
          )
  check_it %>% 
    select(data_model, model_version, cdm, join, filtered, count_filtered)
```
## Filter to find the most matches
```{r}
  check_it %>% 
    select(data_model, model_version, cdm, join, filtered, count_filtered) %>%
    filter(count_filtered == max(count_filtered))
```
True story: 5.2. bugfix 1 and 5.2.2 are functionally identical for postgreSQL and contain the same tables and fields... SUCCESS! With this knowledge, I would suggest removing 5.2 bugfix 1 in favor of 5.2.2, which would be properly detected.

## Extract the table mapping
```{r}
  table_map <- check_it %>% 
    filter(count_filtered == max(count_filtered) & model_version=='v5_2_2') %>% 
    select(data_model, model_version, cdm, join)
  table_map$join
```